---
title: 'GEOG712 Course Project - Assessing the influence of tourists’ perceived travel environment and their travel behavior on travel satisfaction using structural equation models (SEM): a case of Qinghai-Tibet Plateau'
author: 'Haoran Xu'
#date: 'Dec 2024'
university: 'McMaster University'
faculty: 'Faculty of Science'
department: 'School of Earth, Environment and Society'
subject: 'Geography'
instructor: 'Antonio Paez'
bdegree: 'B.Sc.' # Bachellor's Degree
mdegree: ''   # Master's Degree (if any)
degree: 'Doctor of Philosophy'

knit: bookdown::render_book
site: bookdown::bookdown_site

output:
  macdown::thesis_pdf: default 
  keep_tex: true

lay_abstract: |
  The lay abstract must be 150 words or less.
  Hi this is the lay abstract.
  
  It must explain the key goals and contributions of the thesis in lay terms that are accessible to the general public. 
abstract: |
  This paper is the final project work for course GEOG712. It ueses a 
# Note that a tab is needed on the line after the `|`. Subsequent paragraphs need to be indented too.
acknowledgements: |
  I would like to thank Dr. Huaxiong Jiang and my undergrad fellows in old days for helping me with research design and questionnaire distributing. I would also like to thank Dr. Antonio Paez for teaching this course and guiding me throughout the whole semester to learn from scratch about R and Github. With limited coding experiences before, I had been exposed to a lot of new ideas and thoughts on doing research itself. Mostly importantly, I am glad that I got to have the chance to build my own coding space little by little through detailed instructions, and that I could have little more confidence in coding skills instead of anxiety and upset. Anyways, this course surely would shed a very important light in my subsequent years of pursuing a PhD and a possible academic career.
declarations: |
  I did most of the research.
  
  Also the writting. 
  
  Sometimes I cried.
  
  But mostly I had fun.
quotation: 'Hope in 2025 you can code more, better, and with confidence.'
# Author of the quotation
qauthor: 'Haoran'
# Specify the location where the bibliography file is found below
bibliography: bib/thesis.bib
# Download your specific csl file and refer to it in the line below.
csl: csl/apa.csl
lot: true
lof: true
---

```{r include_packages, include = FALSE}
# This chunk ensures that the macdown package is
# installed and loaded. This macdown package includes
# the template files for the thesis.
if(!require(remotes))
  install.packages("remotes", repos = "http://cran.rstudio.com")
if(!require(macdown))
  remotes::install_github("paezha/macdown")
library(macdown)
```

# Preface {.unnumbered}

This r project `TravelBehaviorQinghai` is created by first-year PhD student [Haoran Xu](https://github.com/Horan517) to produce a model paper for the final course project of ["GEOG712 - Reproducible Research Workflow"](https://github.com/paezha/Reproducible-Research-Workflow/tree/master), taught by [Dr. Antonio Paez](https://experts.mcmaster.ca/display/paezha) at McMaster University, Canada.

The paper is titled "Assessing the influence of tourists’ perceived travel environment and their travel behavior on travel satisfaction using structural equation models (SEM): a case of Qinghai-Tibet Plateau", and stems from a half-way done research project in collaboration with [Dr. Huaxiong Jiang](https://www.researchgate.net/scientific-contributions/Huaxiong-Jiang-2157090528) starting from Jun, 2022 from [Beijing Normal Universtiy, China](https://english.bnu.edu.cn/). 
The project paused since March of 2023 due to lack of time and energy investment. Therefore, I am taking the chance of this course project to review and re-arrange the previous work I had done nearly two years ago. Main work I did for this course project include:
  
  - developing an r package using the existing dataset of Excel format, transforming it into reproducible, open-sourced, and well-cleaned .rda format dataset.
  - using r package [lavaan](https://lavaan.ugent.be/) to reproduce the [Structural Equations Modeling](https://en.wikipedia.org/wiki/Structural_equation_modeling) (SEM) method, which was previously constructed and performed with [mplus](https://www.statmodel.com/), a commercial software.
  - writing a model article in r studio using latex syntax, practicing several r packages such as `tidyverse`, `kableExtra`, and `macdown`.

```{r eval=!knitr::is_latex_output(), child=here::here("01-chap1.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("02-chap2.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("03-results.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("04-conclusion.Rmd")}

```

```{r eval=!knitr::is_latex_output(), child=here::here("99-references.Rmd")}

```
